### 2013-06-07 Rcode/intro.rmd
added automatic say to select sigmaavec

beta.ash=ash(ss$betahat,ss$betasd)
#compute the usual zscore and corresponding p value
zscore = ss$betahat/ss$betasd

@@

>>>>

beta.ash=ash(ss$betahat,ss$betasd)
beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)
#compute the usual zscore and corresponding p value
zscore = ss$betahat/ss$betasd

@@

Plot the fitted underlying distribution on top of true values for beta
```{r}
hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-4,4,length=1000)
lines(x,density(beta.ash,x),col=2)
```

[for testing: compare with the results from the automatic way for selecting sigma]
```{r}
hist(ss$beta,prob=TRUE,breaks=seq(-7,7,length=20))
x= seq(-4,4,length=1000)
lines(x,density(beta.ash.auto,x),col=2)
```
